---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# add2xgb

<!-- badges: start -->
[![DOI](https://zenodo.org/badge/200150014.svg)](https://zenodo.org/badge/latestdoi/200150014)
<!-- badges: end -->

The goal of add2xgb is to help translate XGBoost model R object into SQL statement.
In production, I translate model file into a sixty-thousand-line SQL code and run it into impala within 1 minute. Thus, It is fine to do this workflow in the model deployment.

## Installation

The development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JiaxiangBU/add2xgb")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(add2xgb)
## basic example code
```

https://jiaxiangbu.github.io/learn_xgboost/translatein2sql/mtcars_xgboost

## Citations

```{r include=FALSE}
citations <- add2pkg::add_zenodo_citation("README.Rmd")
```

```{r echo=FALSE, results='asis'}
cat(citations$Cite)
```

```{r echo=FALSE, results='asis'}
cat(paste0("```BibTex\n",citations$BibTex,"\n```"))
```

```{r echo=FALSE, results='asis'}
cat(citations$Comments)
```



***

`r add2pkg::add_disclaimer("Roland Stevenson;Jiaxiang Li")`

